\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-22 pldi/draft.tex
Update problem/solution

Provided information about the shell constructs and individual commands and their flags, \sys needs to analyze the given script and identify program fragments that are candidates for parallelization.
To achieve this, it converts sections of the script that are amenable to parallelization into a data-flow graph (DFG) representation.
% Second, \sys defines a dataflow graph model that is suitable for the semantics of the POSIX shell and proposes a set of parallelization optimizations that preserve the behavior of the dataflow graph.
This is a flexible representation that enables a series of local transformations that expose data-parallelism, converting the graph into its parallel equivalent.
%% , in which DFGs indicate the parallelizable regions.
Further transformations compile the DFG back to a parallel script that uses POSIX shell constructs to guide parallelism explicitly---while aiming at preserving the semantics of the sequential program.

Finally, \sys needs to provide correct, high-performance combiners for certain classes commands, and be proactive about (addressing) several practical challenges related to quirks of the \unix environment.
In terms of combiners, \sys offers a set of linkable components for stream splitting and merging;
  these commands live in the \ttt{PATH} and are addressable by name, which means they can be used like (and by) any other commands.
Practical challenges---related to task parallelism, deadlock prevention, and runtime performance---are addressed through a series of constructs that \sys provides.

Returning to the script of Fig.~\ref{fig:example}...\nv{I think we should show fragments of the resulting script}

The next few sections (\S\ref{parallelizability}--\ref{impl}) discuss the details.
% They also outline other, less obvious challenges---such as the synchronization of environment variables, distributed file operation, \etc.

>>>>

\heading{Scripts: Dataflow Graphs}
% \sys first needs to understand the POSIX constructs used to compose larger programs, indicating different levels of candidacy for pararllelization.
To assign a candidacy for parallelization, \sys breaks POSIX constructs into a few broad classes:
 (i) the parallel-composition operator (\ttt{\&}) exposes task parallelism,
 (ii) special commands such as \ttt{xargs} and \ttt{tee} expose data parallelism,
 (iii) the pipe operator (\ttt{|}) is a candidate for both task and data parallelism, and
 (iv)  other composition operators such as \ttt{\&\&}, \ttt{||}, and \ttt{;} are barrier candidates.

Provided information commands and POSIX constructs, \sys needs to analyze the given script and identify program fragments that are candidates for parallelization.
To achieve this, it converts sections of the script that are amenable to parallelization into a data-flow graph (DFG) representation.
% Second, \sys defines a dataflow graph model that is suitable for the semantics of the POSIX shell and proposes a set of parallelization optimizations that preserve the behavior of the dataflow graph.
This is a flexible representation that enables a series of local transformations that expose data-parallelism, converting the graph into its parallel equivalent.
%% , in which DFGs indicate the parallelizable regions.
Further transformations compile the DFG back to a parallel script that uses POSIX shell constructs to guide parallelism explicitly---while aiming at preserving the semantics of the sequential program.

\heading{Implementation: Efficient Primitives}
\sys addresses several practical challenges through a set of constructs it provides---\eg a set of linkable components for stream splitting and merging.
For the vast majority of commands in one of the parallelizable classes, it also provides  a small library of pure fold function implementations.
All these commands live in the \ttt{PATH} and are addressable by name, which means they can be used like (and by) any other commands.

Fig~\ref{fig:example2} shows a fragment of \sys's output for the script in Fig.~\ref{fig:example}.
The next few sections (\S\ref{parallelizability}--\ref{impl}) discuss the details.
% They also outline other, less obvious challenges---such as the synchronization of environment variables, distributed file operation, \etc.

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_example2.pdf}}
\caption{
  \textbf{\sys's $2\times$-parallel output for part of Fig.~\ref{fig:example}.}
  \sys orchestrates the script's parallel execution through named pipes, parallel operators and careful placement of combiners.
}
\vspace{-15pt}
\label{fig:example2}
\end{figure}
